---
title: "SRT411A0.Rmd"
author: "PhilKing-SozBroz"
output: html_document
---
>In this assignment we learned how work with R in simple scenarios.   I only used the provided "A (very) short introduction to R".


###Todo 1
```{r}
((2017-2015)/(2017-1994))*100
```
###Todo 2 
```{r}
currentyear=2017
bornyear=1994
unistartyear=2015
((currentyear-unistartyear)/(currentyear-bornyear))*100
rm(list=ls())
```
###Todo 3
```{r}
td3<-(c(4,5,8,11))
sum(td3)
```
###Todo 4
```{r}
td3<-(c(4,5,8,11))
sum(td3)
```
###Todo 5
```{r}
?sqrt
```
###Todo 6
```{r}
plot(rnorm(100))
```

###Todo 7
```{r}
P=c(seq(31,60)) #seq(31:60)
Q<-matrix(data=P,ncol=5)
```
###Todo 8
```{r}
x1<-rnorm(100)
x2<-rnorm(100)
x3<-rnorm(100)
t<-data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
#The plotting is generating the combinations of points when combining the values from the 3 lists to 
#create 2 seperate x,y coordinates
sd(t$a)
sd(t$b)
sd(t$c)
```
###Todo 9
#####rgb (red,green,blue) sets the color
#####lwd (line width) sets the line width 
#####pch (plotting 'character') chooses the symbol to use
#####cex (character expansion) chooses the size of the symbol

```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
#rgb (red,green,blue) sets the color
#lwd (line width) sets the line width 
#pch (plotting 'character') chooses the symbol to use
#cex (character expansion) chooses the size of the symbol
```
###Todo 10
```{r}
temp<-read.table(file="tst1.txt",header=TRUE)
temp$g<-temp$g*5
write.table(temp,file="tst2.txt",row.names=TRUE)
read.table(file="tst1.txt",header=TRUE)
```
###Todo 11
#It prints NaN as some of the random numbers are bound to be negative
```{r}
mean(sqrt(rnorm(100)))
```
###Todo 12
```{r}
pres=c(0,4,5)
date1=strptime(c("20170130","20171225","20170728"), format="%Y%m%d")
barplot(pres, names.arg=(date1))
```


###Todo 13
```{r}
l=c()
for(i in 1:100){
  if(i<5 | i>90){
    l[i]<-i*5
  }else{
    l[i]<-i*0.1
  }
  
}
l
```
###Todo 14
```{r}
lapply(c(1:50),function(v){
  if(v<5 | v>90){
      v<-v*5
    }else{
      v<-v*0.1
    }
  
  }
)
```